Automatic Identification and Annotation of Tasks in Structured Programs

### 2018-02-06 docs/ACM/paper.tex
Fixed Jacobi analysis

\pedro{In the Kenjiro's paper: "This scheduling policy suffers in two situations: 
(1) the parent is a long for loop creating a large number of children, 
all these children cannot start until the parent finishes the task-generating loop (SparseLU); 
(2) binary recursions that, rightly, spawn only the first recursive call as a task (FFT). 
It imposes an upper bound for the ready task queue of a worker; a worker 
is discouraged to create too many tasks ready on the queue"}.

@@

Consider the FFT example, shown in Figure X.

@@

>>>>

%\pedro{In the Kenjiro's paper: "This scheduling policy suffers in two situations: 
%(1) the parent is a long for loop creating a large number of children, 
%all these children cannot start until the parent finishes the task-generating loop (SparseLU); 
%(2) binary recursions that, rightly, spawn only the first recursive call as a task (FFT). 
%It imposes an upper bound for the ready task queue of a worker; a worker 
%is discouraged to create too many tasks ready on the queue"}.

@@

Consider the FIB

@@

\begin{table}[h]
\centering
\caption{Different kinds of tasks among the BOTS benchmarks. {\Taskminer}'s versaitily allows the user to define which type of tasks should be mined, annotated or cared for.}
\label{tab:types}
\begin{tabular}{|r|c|c|c|}
\hline
                   & \textbf{Recursive} & \textbf{FunctionCall} & \textbf{Region} \\ \hline
\textbf{fft}       & \checkmark         &                       & \checkmark      \\ \hline
\textbf{fib}       & \checkmark         &                       &                 \\ \hline
\textbf{floorplan} & \checkmark         &                       & \checkmark      \\ \hline
\textbf{sort}      & \checkmark         &                       & \checkmark      \\ \hline
\textbf{sparselu}  &                    & \checkmark            & \checkmark      \\ \hline
\textbf{strassen}  & \checkmark         &                       & \checkmark      \\ \hline
\textbf{uts}       & \checkmark         &                       &                 \\ \hline
\textbf{nqueens}   & \checkmark         &                       & \checkmark      \\ \hline
\textbf{knapsack}  & \checkmark         &                       & \checkmark      \\ \hline
\textbf{health}    & \checkmark         & \checkmark            & \checkmark      \\ \hline
\textbf{jacobi}    &                    &                       &                 \\ \hline
\end{tabular}
\end{table}
